Transfer Learning in Visual and Relational Reasoning

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/related_work.tex
Added small paragraph about TL in Visual Reasoning in Related Works.

\section{Related work}

\tk{That section will focus \textbf{only} on transfer learning}

In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as segmentation of cars~\cite{iglovikov2018ternausnet} or Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging}.
Such performance improvements are appealing, especially in cases where both the domain (natural vs. medical images) and the task (image classification vs. image segmentation vs VQA) change significantly. %This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.

@@

\tk{missing review: TL in visual reasoning, refer to CoGenT and COG}

>>>>

\section{Related work}
\label{sec:related_work}

In Computer Vision, it is now standard practice to pretrain an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as segmentation of cars~\cite{iglovikov2018ternausnet} or Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging}.
Such performance improvements are appealing, especially in cases where both the domain (natural vs. medical images) and the task (image classification vs. image segmentation vs VQA) change significantly.

@@

In Visual Reasoning, transfer learning has helped models generalize better to domains with different distributions. Using the CLEVR-CoGenT~\cite{johnson2017clevr} dataset and finetuning, \cite{mascharka2018transparency, perez2018film, johnson2017inferring} have demonstrated impressive accuracy gains on a domain with different attributes combinations than the one used for training. Similarly, using the COG dataset, \cite{yang2018dataset} have shown that a model can do significantly better than chance on a task it was not explicitly trained on, by using knowledge learned on other tasks.
